A simple model of urban evolution based on innovation diffusion

### 2020-04-29 Docs/Papers/EvolutionInnovation/paper.tex
run_model

The principal idea in the model is to build on a concept of ``Urban DNA'' which would capture evolution processes as in biological evolution and cultural evolution, i.e. a kind of genome that cities would be exchanging and which would undergo mutation processes. A suitable candidate is to build on the concept of \emph{meme} introduced in the field of cultural evolution. However, several particularities must be stressed out when working with urban systems.

>>>>

The core idea of the model is to build on a concept of ``Urban DNA'' which would capture evolution processes as in biological evolution and cultural evolution, i.e. a kind of genome that cities would be exchanging and which would undergo mutation processes. A suitable candidate is to build on the concept of \emph{meme} introduced in the field of cultural evolution. However, several particularities must be stressed out when working with urban systems.
